An investigation of times that a lack in good physical security practices led to a cyber security issue

### 2024-02-12 Paper/Paper.tex
Fix typo
More work on essay

\documentclass[acmsmall]{acmart}

@@

\acmYear{2024}
\acmDOI{cybersecurity.tomcruise}
\acmJournal{TISSEC}
\acmVolume{420}
\acmNumber{69}
\acmArticle{3.14}
\acmMonth{1}

\setcopyright{acmlicensed}
\copyrightyear{2024}
\begin{document}

\title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}

@@

\begin{abstract}
  Cybersecurity requires many layers and aspects of security to achieved.
  This article analyzes and reviews historical occurences where a lack of
  physical security lead to a lack of cybersecurity. In addition to introduction,
  an analysis and review of such occurences will be presented.
\end{abstract}

@@

\maketitle

\section{Introduction}
In the world of software and programs, many people in the cybersecurity
field focus on the security and practices used in their software and programs.
However, one of the most well-known ideas for security is the idea that
your security is only as strong as your weakest link. Just as electricity
follows the path of least resistance, hackers and cybercriminals need only
find a single weak point in your security to gain access to the rest of
your system.

@@

\section{Basic Physical Security}
Regardless of what a device is doing, it is always important to understand
the physical environment and security that the device is in. Even the
best anti-virus software cannot be protected from a malicious actor
uninstalling it. Physical access could mean a man in the middle attack,
power outages, or even a keylogger being installed.

@@

\section{Google's Plasma Globe \texorpdfstring{\cite{Google01}}{}}
One of the best ways to test your security is by doing it yourself. Google
went about this by creating a "Red Team", a team of white-hat hackers that
were tasked with trying to hack Google. Though this task certainly includes
doing software-based attacks, one of the successful attacks was actually
a physical attack.

\subsection{Attack}
The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
Only five plasma globes were created with a malicious modification to them.
The Red Team added an internal chip that would emulate a USB keyboard when plugged
in to a computer. After approximately 5-10 minutes \cite{lcamtuf}, the device
would quickly type out a command to download a larger payload from the internet.
In order to give the device to Google's employees, the Red Team disguised the
device as an anniversary gift from Google (based off of LinkedIn).

While not everyone that received the device plugged it in, it only took one of
Google's employees to plug it in for the attack be successful. Upon successful
execution of the script, the Red Team had access to the employee's credentials.
Through this, they were able to send emails to other employees which had higher
privileges. Through these emails with attachments, the Red Team was able to
gain access to Google's Glasses internal documentation.

Finally, the Red Team attempted to obtain a physical build of the Google Glasses.
Unfortunately, due to a few typos, the Red Team caused a few red flags to be raised,
and instead of going to pick up the build, they were met with Google's Chief Security
Officer.

\subsection{Analysis}
What ultimately allowed this attack to be successful was improper training, understanding,
and awareness of physical security. Google's employees were not trained to be aware
of the potential dangers of plugging in a USB device was given to them.

@@

\subsection{Attack}
While very entertaining, the attack in the movie is not entirely realistic. Quick uniform
changes and pretending that you belong was presented to seem entirely plausible. Regardless,
the important parts of the attack were that the server room was easily accessible by all staff
without only one layer of security. The single layer was a wired door that was left open
by the original server maintainer.

@@

\subsection{Attack}
In the movie, we are shown the many physical layers of security that the CIA
building has. The building has a security guard, a security camera, a keycard
reader, and a physical key. Access to the NOC list is also restricted to only
the physical computer that the NOC list is on. The server room employs many
measures and monitors to prevent unauthorized access.

@@

\section{Conclusion}
We have seen examples of physical security and how attackers may navigate around
it. Being aware of all potential entrypoints and the human element of security is important
to keep in mind when designing a secure system. Security exploits could stem from the
design of a building (such as a server room being too accessible) to the training of
its employees.

>>>>

\documentclass[acmsmall]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

@@

\acmYear{2024}
\acmDOI{cybersecurity.tomcruise}
\acmJournal{TISSEC}
\acmVolume{420}
\acmNumber{69}
% \acmArticle{3.14}
\acmMonth{1}

\setcopyright{acmlicensed}
\copyrightyear{2024}

\begin{document}

% \title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
\title{An investigation of times that a lack in good physical security practices led to a cyber security issue}

@@

\begin{abstract}
  Cybersecurity involves many layers and aspects of security to be achieved.
  This article analyzes and reviews historical occurences where a lack of
  physical security lead to a lack of cybersecurity. In addition to introduction,
  an analysis and review of such occurences will be presented.
\end{abstract}

@@

\maketitle
\fancyfoot{}
\thispagestyle{empty}

\section{Article Introduction}
In the world of software and programs, many people in the cybersecurity
field focus on the security and practices used in their software and programs.
However, one of the most well-known ideas for security is the idea that
a system's security is only as strong as its weakest link. Just as electricity
follows the path of least resistance, hackers and cybercriminals need only
find a single weak point in a system to gain access to the rest of
it.

@@

A potential opinion of cybersecurity could fail to see (or underestimate) how
a company's corporate culture could impact the security of the company.
Password policies, access control, logging, and properly following
security procedures must stem from a cybersecure-forward culture.

\section{Physical Security}
Regardless of what a device is doing, it is always important to understand
the physical environment and security that the device is in. Even the
best anti-virus software cannot be protected from a malicious actor
uninstalling it. Physical access could mean a man in the middle attack,
power outages, or even a keylogger being installed.

@@

\subsection{Cyber Secure Culture and Physical Security}
The importance of a cyber secure culture cannot be understated. A company
that does not have a cyber secure culture will not have employees that
are aware of the dangers of social engineering, phishing, or plugging in
unauthorized devices.

Employee training, security protocols, and procedures are all dependent
on a culture that is aware, attentive, and proactive about security;
which you can only get from a cyber secure culture.

For instance, Google's Cyber Security Culture is stringent on including
physical security, one example being how they handle their data centers \cite{GoogleData}.
Google made a video describing the security of their centers. To emphasize why
the culture of cyber-security is important,
Stephanie Wong (a Google employee) admitted she "could talk all day
about cloud security, (but)physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.

Google's Data Centers are a good example of how physical security is an important
aspect of cybersecurity.

\section{Google's Plasma Globe}
One of the best ways to test security is by testing, verifying, and self-auditing
how well the security system holds up. Google went about this by creating a
"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with trying to hack Google.
Though this task certainly includes doing software-based attacks, one of the successful
attacks was a physical attack.

\subsection{Google's Plan of Attack}
The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
Only five plasma globes were created with a malicious modification to them.
The Red Team added an internal chip that would emulate a USB keyboard when plugged
in to a computer. After approximately 5-10 minutes, the device would
quickly type out a command to download a larger payload from the internet \cite{GoogleGlobeBlog}.
In order to give the device to Google's employees, the Red Team disguised the
device as an anniversary gift from Google (based off of LinkedIn).

While not everyone that received the device plugged it in, it only took one of
Google's employees to plug it in for the attack be successful. Upon successful
execution of the script, the Red Team had access to the employee's credentials.
Through this, they were able to send emails to other employees which had higher
privileges. Through these emails with attachments, the Red Team was able to
gain access to Google's Glasses internal documentation \cite{GoogleGlobeVideo}.

Finally, the Red Team attempted to obtain a physical build of the Google Glasses.
Unfortunately, due to a few typos, the Red Team caused a few red flags to be raised,
and instead of going to pick up the build, they were met with Google's Chief Security
Officer \cite{GoogleGlobeVideo}.

\subsection{Attack Analysis}
Ultimately, this attack was a phishing attack. The Red Team was able to convince
Google's employees to plug in a USB device that was given to them. The Red Team
was able to gain access to Google's Glasses internal documentation by using the
employee's credentials.

Google's physical security culture did not account for the dangers of plugging in
unauthorized devices. While Google's employees may have been aware of the dangers
of USB devices, mistakes can happen or people can forget about security.
Re-inforcing the importance of a cyber secure culture and the dangers of social
engineering is important.

@@

\subsection{Attack}
While very entertaining, the attack in the movie is not entirely realistic. Quick uniform
changes and pretending that you belong was presented to seem entirely plausible. Regardless,
the important parts of the attack were that the server room was easily accessible by all staff
with only one layer of security. The single layer was a wired door that was left open
by the original server maintainer.

@@

\subsection{Attack}
The move shows the many physical layers of security that the CIA
building has. The building has a security guard, a security camera, a keycard
reader, and a physical key. Access to the NOC list is also restricted to only
the physical computer that the NOC list is on. The server room employs many
measures and monitors to prevent unauthorized access.

@@

\section{Conclusion}
Being aware of all potential entrypoints and the human element of security is important
to keep in mind when designing a secure system. Security exploits could stem from the
design of a building (such as a server room being too accessible) to the training of
its employees.
